---
title: "Criação de Mapas no R"
subtitle: "com geobr, ggplot, plotly"
author: "[Prof. Steven Dutt-Ross](https://dataunirio.github.io/site_pessoal/)"
categories: ["R"]
tags: ["R Markdown", "Mapas"]
output:
  xaringan::moon_reader:
    lib_dir: libs
    chakra: libs/remark-latest.min.js
    css: [default, hygge, ninjutsu]
    nature:
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---


```{r, include = F}

# https://www.rstudio.com/blog/building-code-movies-with-flipbookr/
# https://evamaerey.github.io/flipbooks/flipbook_recipes#1
#
# This is the recommended set up for flipbooks
# you might think about setting cache to TRUE as you gain practice --- building flipbooks from scratch can be time consuming
knitr::opts_chunk$set(fig.width = 6, message = FALSE, warning = FALSE, comment = "", cache = F)
library(flipbookr)
library(tidyverse)
```


```{css, eval = TRUE, echo = FALSE}
.remark-code{line-height: 1.5; font-size: 80%}

@media print {
  .has-continuation {
    display: block;
  }
}


code.r.hljs.remark-code{
  position: relative;
  overflow-x: hidden;
}


code.r.hljs.remark-code:hover{
  overflow-x:visible;
  width: 500px;
  border-style: solid;
}
```

```{r xaringan-themer, include=FALSE}
library(xaringanthemer)
style_duo_accent(
  # primary_color = "#345865",
  primary_color = "#B56B6F",
  secondary_color = "#2c8475",
  black_color = "#4242424",
  white_color = "#FFF",
  base_font_size = "25px",
  # text_font_family = "Jost",
  # text_font_url = "https://indestructibletype.com/fonts/Jost.css",
  header_font_google = google_font("Roboto Slab", "400", "700"),
  header_font_weight = "400",
  inverse_header_color = "#eaeaea",
  title_slide_text_color = "#FFFFFF",
  text_slide_number_color = "#9a9a9a",
  text_bold_color = "#f79334",
  code_inline_color = "#B56B6F",
  code_highlight_color = "transparent",
  link_color = "#2c8475",
  table_row_even_background_color = lighten_color("#345865", 0.9),
  extra_fonts = list(
    "https://indestructibletype.com/fonts/Jost.css",
    google_font("Amatic SC", "400")
  ),
  colors = c(
    green = "#31b09e",
    "green-dark" = "#2c8475",
    highlight = "#87f9bb",
    purple = "#887ba3",
    pink = "#B56B6F",
    orange = "#f79334",
    red = "#dc322f",
    `blue-dark` = "#002b36",
    `text-dark` = "#202020",
    `text-darkish` = "#424242",
    `text-mild` = "#606060",
    `text-light` = "#9a9a9a",
    `text-lightest` = "#eaeaea"
  ),
  extra_css = list(
    ".remark-slide-content h3" = list(
      "margin-bottom" = 0, 
      "margin-top" = 0
    ),
    ".smallish, .smallish .remark-code-line" = list(`font-size` = "0.9em")
  )
)
#library(xaringanExtra)
#xaringanExtra::use_xaringan_extra(c("animate_css")
#xaringanExtra::use_extra_styles()
```

# Hi!

--

This 'minimal flipbook' template has a couple of classic examples to get you building your first flipbooks!

--

flipbooks are code-movies.  The frames of the movies are slides. Here we use the R package {xaringan} to create a remark.js slideshow. 

--

Slide breaks are indicated with `---` (be careful trailing white space is not allowed)

--

flipbookr's `chunk_reveal()` disassembles a single code chunk and creates the "build" of multiple partial-code chunks on different slides (the --- is automatically generated for you too).  

--

We use `chunk_reveal()` it 'inline', not in a code chunk. 

--

Let's start!



---
class: inverse, middle, center


# First up: classic flipbook, using defaults to walk through code pipeline



```{r meus_dados, include = FALSE}

url_do_arquivo <- "https://github.com/DATAUNIRIO/Base_de_dados/raw/master/BasesEstados.xlsx"
url_do_arquivo
download.file(url_do_arquivo,"BasesEstados.xlsx",mode="wb") 
library(readxl)
dados_brutos <- read_excel("BasesEstados.xlsx")
head(dados_brutos)

```

`r chunk_reveal("meus_dados", title = "### Carregar a base de dados")`


---
class: inverse, center, middle

# Next up:  refer to same chunk, but use user defined breakpoints, and display output only




---
class: inverse, center, middle

# Next up:  cycle through different lines of code



```{r meu_mapa, eval = T, echo = T,message=FALSE,comment=NA}

library(geobr)
mapa_estados <- read_state()

```


---
class: inverse, center, middle


```{r meu_mapa2, eval = F, echo = F}

head(mapa_estados)

```


`r chunk_reveal("meu_mapa2", title = "### Inspecionar o mapa")`




---

# Notes: 

- This minimal flipbook assumes you are online when you build and view.  It is going to find the most recent remark.js info online.

- xaringan/remark.js slideshows are not self contained, single file slide shows.  Make sure you ship all the associated files that are created to display your flipbooks/slideshows.  I like to push .html and associated files to github repository and use Github Pages to host for beyond local sharing. :-)

